Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection

### 2017-03-24 paper/presentation/DASFAA_presentation.tex
first three pages

@@

%------------------------------
%page 3
\begin{frame}
\frametitle{Challenges (1/2)}
What we have already known:

What we maybe know, but didn't pay much attention:

@@

%------------------------------
%page 4
\begin{frame}
\frametitle{Challenges (2/2)}	
\tikzmark{comment18}\,

\intextsep=5pt plus 3pt minus 1pt % 调整表格与正文的上间距
\begin{table}[]
\setlength{\abovecaptionskip}{0.cm}%set the distance between caption and table to 0 cm.
\setlength{\belowcaptionskip}{0.cm}
\centering
\caption{Statistics of labeled events on Edinburgh twitter corpus.}
\label{my-label}
\scalebox{0.65}{
\begin{tabular}{|l|l|r|}
\hline
Event                                        & Date       & Event Size \\ \hline
S\&P downgrade US credit rating                  & 05/08/2011 & 656      \\ \hline
Atlantis shuttle lands                           & 21/07/2011 & 595      \\ \hline
US increases debt ceiling                        & 25/07/2011 & 485      \\ \hline
Plane with Russian hocky team Lokomotiv crashes  & 07/09/2011 & 286      \\ \hline
Amy Winehouse dies                               & 23/07/2011 & 283      \\ \hline
Gunman opens fire in youth camp in Norway        & 23/07/2011 & 260      \\ \hline
Earthquake in Virginia                           & 24/08/2011 & 246      \\ \hline
First victim of London riots dies                & 09/08/2011 & 174      \\ \hline
Explosion in French nuclear plant in Marcoule    & 12/09/2011 & 135      \\ \hline
Google announces plans to bury Motorola Mobility & 15/08/2011 & 127      \\ \hline
NASA announces there might be water on Mars      & 04/08/2011 & 124      \\ \hline
Car bomb explodes in Oslo, Norway                & 22/07/2011 & 114      \\ \hline
... & ... & ... \\ \hline
\tikzmarkin<1>[hl]{bH1}Indian and Bangladesh sign a border pact         & 06/09/2011 & 25       \\ \hline
Flight 4896 crash                                & 13/07/2011 & 21       \\ \hline
First aritficial organ transplant                & 12/07/2011 & 18       \\ \hline
three men die in riots in england                & 10/08/2011 & 16       \\ \hline
rebels capture interational tripoli airport      & 21/08/2011 & 13       \tikzmarkend{bH1} \\ \hline
\end{tabular}
}
\end{table}

 \begin{textblock}{0.1}(14,12)
  \footnotesize{Small events with fewer tweets}
 \end{textblock}

>>>>

%use bold arrow
\usepackage{marvosym}

@@

%------------------------------
%page 3
\begin{frame}
\frametitle{Challenges (1/2)}
According to [Huang, WWW 2016], the challenges include,
\begin{enumerate}
\item fast changing
\item high noise
\item short length
\end{enumerate}

\vfill

And, we found another key factor, 
\begin{enumerate}
\item Small events with fewer tweets \MVRightarrow \ \ Hard to trade off between precision and recall. 
\end{enumerate}

@@

%------------------------------
%page 4
\begin{frame}
\frametitle{Challenges (2/2)}	
Exploratory study on the on Edinburgh twitter corpus: 11/29 events contains less than 50 tweets.

\intextsep=5pt plus 3pt minus 1pt % 调整表格与正文的上间距
\begin{table}[]
\setlength{\abovecaptionskip}{0.cm}%set the distance between caption and table to 0 cm.
\setlength{\belowcaptionskip}{0.cm}
\centering
\caption{Statistics of labeled events.}
\label{my-label}
\scalebox{0.65}{
\begin{tabular}{|l|l|r|}
\hline
Event                                        & Date       & Event Size \\ \hline
S\&P downgrade US credit rating                  & 05/08/2011 & 656      \\ \hline
Atlantis shuttle lands                           & 21/07/2011 & 595      \\ \hline
US increases debt ceiling                        & 25/07/2011 & 485      \\ \hline
Plane with Russian hocky team Lokomotiv crashes  & 07/09/2011 & 286      \\ \hline
Amy Winehouse dies                               & 23/07/2011 & 283      \\ \hline
Gunman opens fire in youth camp in Norway        & 23/07/2011 & 260      \\ \hline
Earthquake in Virginia                           & 24/08/2011 & 246      \\ \hline
First victim of London riots dies                & 09/08/2011 & 174      \\ \hline
Explosion in French nuclear plant in Marcoule    & 12/09/2011 & 135      \\ \hline
Google announces plans to bury Motorola Mobility & 15/08/2011 & 127      \\ \hline
NASA announces there might be water on Mars      & 04/08/2011 & 124      \\ \hline
Car bomb explodes in Oslo, Norway                & 22/07/2011 & 114      \\ \hline
... & ... & ... \\ \hline
\tikzmarkin<1>[hl]{bH1}Indian and Bangladesh sign a border pact         & 06/09/2011 & 25       \\ \hline
Flight 4896 crash                                & 13/07/2011 & 21       \\ \hline
First aritficial organ transplant                & 12/07/2011 & 18       \\ \hline
three men die in riots in england                & 10/08/2011 & 16       \\ \hline
rebels capture interational tripoli airport      & 21/08/2011 & 13       \tikzmarkend{bH1} \\ \hline
\end{tabular}
}
\end{table}

 \begin{textblock}{0.1}(13.5,11.7)
  \footnotesize{11 Small events with fewer tweets}
 \end{textblock}
